\textbf{{\Large {System of dual functions in the reduction of affine Lie algebra representations}}}

### 2010-08-03 AffineLieAlgebras/DualFunctions/article.tex
The problem is how to enumerate weights inside the main Weyl chamber?

\section{Finite-dimensional Lie algebras}
\label{sec:finite-dimens-lie}
Consider the irreducible highest-weight module $L^{(\mu)}_{\mathfrak{g}}$ of the simple Lie algebra $\mathfrak{g}$. 
The recurrent relation for the weight multiplicities can be written from the Weyl character formula \cite{lyakhovsky1996rra}:
\begin{equation}
  \label{eq:1}
  \mathrm{ch} L^{(\mu)}_{\mathfrak{g}}=\frac{\sum_{w\in W}\epsilon(w) e^{w(\mu+\rho)-\rho}}{\sum_{w\in W}\epsilon(w) e^{w \rho -\rho}}
\end{equation}
Let us limit our consideration to the fundamental domain (main Weyl chamber). The left side of this equation can be written as
\begin{equation}
  \label{eq:2}
   \mathrm{ch} L^{(\mu)}_{\mathfrak{g}}=\sum_{\lambda\in \bar{C}_{\mathfrak{g}}} m^{(\mu)}_{\lambda} e^{\lambda}
\end{equation}
Multiplying the equation \eqref{eq:1} by the denominator  and collecting the common terms we get the recurrent relation for the weight multiplicities $m^{(\mu)}_{\lambda}$:
\begin{equation}
  \label{eq:3}
  \sum_{w\in W} \epsilon(w) m^{(\mu)}_{\lambda-w\rho+\rho}=\sum_{w\in W}\epsilon(w) \delta_{\lambda,w(\mu+\rho)-\rho}
\end{equation}
\section{Affine Lie algebras}
\label{sec:affine-lie-algebras}

>>>>

\section{Finite-dimensional Lie algebras}
\label{sec:finite-dimens-lie}
Consider the irreducible highest-weight module $L^{(\mu)}_{\mathfrak{g}}$ of the simple Lie algebra $\mathfrak{g}$. 
The recurrent relation for the weight multiplicities can be written from the Weyl character formula \cite{lyakhovsky1996rra}:
\begin{equation}
  \label{eq:1}
  \mathrm{ch} L^{(\mu)}_{\mathfrak{g}}=\frac{\sum_{w\in W}\epsilon(w) e^{w(\mu+\rho)-\rho}}{\sum_{w\in W}\epsilon(w) e^{w \rho -\rho}}
\end{equation}
Let us limit our consideration to the fundamental domain (main Weyl chamber). The left side of this equation can be written as
\begin{equation}
  \label{eq:2}
   \mathrm{ch} L^{(\mu)}_{\mathfrak{g}}=\sum_{\lambda\in \bar{C}_{\mathfrak{g}}} m^{(\mu)}_{\lambda} e^{\lambda}
\end{equation}
Multiplying the equation \eqref{eq:1} by the denominator  and collecting the common terms we get the recurrent relation for the weight multiplicities $m^{(\mu)}_{\lambda}$:
\begin{equation}
  \label{eq:3}
  \sum_{w\in W} \epsilon(w) m^{(\mu)}_{\lambda-w\rho+\rho}=\sum_{w\in W}\epsilon(w) \delta_{\lambda,w(\mu+\rho)-\rho}
\end{equation}
If we consider the weights inside the main Weyl chamber the sum on the right-hand side is reduced to the single term $\delta_{\lambda,\mu}$. For the weight $\lambda-w\rho+\rho\not\in \bar{C}_{\mathfrak{g}}$ there exists weight $\xi\in \bar{C}_{\mathfrak{g}}$ and Weyl group element $v\in W$ such that $v\xi=\lambda-w\rho+\rho$, so we can limit the computation of weight multiplicities by the main Weyl chamber. This procedure was called ``folding of the fan'' in \cite{il2010folded}.
Now we want to rewrite the equation \eqref{eq:3} in matrix form similarly to \cite{2010arXiv1001.3683N}.
We need to choose the ordering on the set of weights in the closure of fundamental domain $\bar{C}_{\mathfrak{g}}$. We use the following procedure. Consider some ordering of the simple roots (e.g. the numbering of nodes of Dynkin diagram from left to right). Then the weight with the Dynkin labels $[0,\dots,0]$ get the index 1, $[0,\dots,0,1]$ the index 2, $[0,\dots,0,1,0]$ - 3 etc.
\section{Affine Lie algebras}
\label{sec:affine-lie-algebras}
